Testing Traversability of Protein Tunnels with Flexible Ligands Using Motion Planning

### 2017-06-15 paper.tex
images of confomrations

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[ruled,lined]{algorithm2e}
\usepackage{multirow}
\usepackage[bookmarks=false]{hyperref}
\pdfminorversion=4

@@

\institute{
    V. Von\'{a}sek, Martin Saska \at 
    Faculty of Electrical Engineering,  
Czech Technical University in Prague, 
Technick\'a 2, 166 27, Prague 6, Czech Republic
\email{vonasek@labe.felk.cvut.cz}  
\and
B. Kozl\'{\i}kov\'{a}, A. Jur\v{c}\'{\i}k \at
Faculty of Informatics,  
Masaryk University, 
Botanick\'a 68a, 602 00 Brno, \\
\and 
David Bedn\'{a}\v{r} \at 
Faculty of Science,
Masaryk University,
Kamenice 5, 625 00 Brno
}

@@

\section{Preliminaries}

@@

\section{Ligand traversability}

@@

\def\tmpa{0.16\textwidth}

\begin{figure}
\centering
\begin{tabular}{cccccc}
\includegraphics[width=\tmpa]{fig/m003-000} &
\includegraphics[width=\tmpa]{fig/m003-001} &
\includegraphics[width=\tmpa]{fig/m003-002} & 
\includegraphics[width=\tmpa]{fig/m003-003} & 
\includegraphics[width=\tmpa]{fig/m003-004} & 
\includegraphics[width=\tmpa]{fig/m003-005} \\
\includegraphics[width=\tmpa]{fig/m003-006} &
\includegraphics[width=\tmpa]{fig/m003-007} &
\includegraphics[width=\tmpa]{fig/m003-008} & 
\includegraphics[width=\tmpa]{fig/m003-009} & 
\includegraphics[width=\tmpa]{fig/m003-010} & 
\includegraphics[width=\tmpa]{fig/m003-011} \\
\end{tabular}
\caption{todo and maybe delete}
\end{figure}

\section{Visualization of results}

@@

To present the results to chemists ...

@@

The proposed method has been used to analyze a tunnel in Haloalkane dehalogenase (protein 1CQW) (Fig.~\ref{fig::tunnel}).
The tunnel was computed using CAVER 3.0~\cite{caver3} for spherical probe of radius 0.9~\AA.
The tunnel is represented by 760 spheres with average distance $0.05$~\AA.

% from David: m003 je "1-chlorpropan" a m004 "1-chlorbutan"
The traversability of the tunnel was evaluated for 1-chlorpropan (denoted as $\LA$) and 1-chlorbutan (denoted as $\LB$).

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{fig/protein-tunnel-gray}
\caption{\label{fig::tunnel}
    The protein 1CQW visualized using its secondary structure (gray) with its highest ranked tunnel (green) which was detected using CAVER 3.0.
}
\end{figure}

>>>>

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{subfig}
\usepackage[ruled,lined]{algorithm2e}
\usepackage{multirow}
\usepackage[bookmarks=false]{hyperref}
\pdfminorversion=4

@@

\institute{
    V. Von\'{a}sek, Martin Saska:
    Faculty of Electrical Engineering,  
Czech Technical University in Prague, 
Technick\'a 2, 166 27 Prague, Czech Republic
\email{vonasek@labe.felk.cvut.cz}   \\
%\and
B. Kozl\'{\i}kov\'{a}, A. Jur\v{c}\'{\i}k:
Faculty of Informatics,  
Masaryk University, 
Botanick\'a 68a, 602 00 Brno, \\
%w\and 
David Bedn\'{a}\v{r}:
Faculty of Science,
Masaryk University,
Kamenice 5, 625 00 Brno\\
The presented work has been supported by the Czech Science Foundation (GA{\v C}R) under research project No. 17-07690S.
Access to computing and storage facilities owned by parties and projects contributing to the National Grid Infrastructure MetaCentrum, provided under the programme "Projects of Large Infrastructure for Research, Development, and Innovations" (LM2010005), is greatly appreciated.
}

@@

%\section{Preliminaries}
\section{Traversability in tunnels}

\subsection{Preliminaries}

@@

\subsection{Motion planning}

%\section{Ligand traversability}

@@

%\begin{figure}
%\centering
%\begin{tabular}{cccccc}
%\includegraphics[width=\tmpa]{fig/m003-000} &
%\includegraphics[width=\tmpa]{fig/m003-001} &
%\includegraphics[width=\tmpa]{fig/m003-002} & 
%\includegraphics[width=\tmpa]{fig/m003-003} & 
%\includegraphics[width=\tmpa]{fig/m003-004} & 
%\includegraphics[width=\tmpa]{fig/m003-005} \\
%\includegraphics[width=\tmpa]{fig/m003-006} &
%\includegraphics[width=\tmpa]{fig/m003-007} &
%\includegraphics[width=\tmpa]{fig/m003-008} & 
%\includegraphics[width=\tmpa]{fig/m003-009} & 
%\includegraphics[width=\tmpa]{fig/m003-010} & 
%\includegraphics[width=\tmpa]{fig/m003-011} \\
%\end{tabular}
%\caption{todo and maybe delete}
%\end{figure}
%

\subsection{Visualization of results}

@@

@@

The proposed method has been used to analyze a tunnel in Haloalkane dehalogenase (protein 1CQW) (Fig.~\ref{fig::tunnel}a).
The tunnel was computed using CAVER 3.0~\cite{caver3} for spherical probe of radius 0.9~\AA.
The tunnel is represented by 760 spheres with average distance $0.05$~\AA.
% from David: m003 je "1-chlorpropan" a m004 "1-chlorbutan"
The traversability of the tunnel was evaluated for 1-chlorpropan (denoted as $\LA$) and 1-chlorbutan (denoted as $\LB$).
$\LA$ was represented by 12 conformations, and $\LB$ by a set of $114$ conformations.
Examples of three conformations are depicted in Fig.~\ref{fig::tunnel}b.

The tested ligands are bigger than the tunnel with, therefore the ligands have been scaled down, and four
different scales were used: $\smin=\{0.3,0.4,0.5,0.6\}$.
For each of this scale, 50 collision-free initial states were found in the $2$\AA radius of the first sphere of the tunnel.
For each ligand, each minimal scale $\smin$ and each start configuration, 100 trajectories were computed using the proposed planner.
The parameters of the planner are: $\Imax=10000$, $m=50$, $\gb=0.9$, $\dt=1.5$\AA.

The average runtimes and sizes of the build tree are shown in Tab.~\ref{tab::rrt}.
For each trajectory

\def\tmpa{0.13\textwidth}

\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[width=0.38\textwidth]{fig/protein-tunnel-gray} &
\includegraphics[width=0.5\textwidth]{fig/ligAll}  \\
(a) & (b)                        
\end{tabular}                       
\caption{\label{fig::tunnel}
    (a) The protein 1CQW visualized using its secondary structure (gray) with its highest ranked tunnel (green) which was detected using CAVER 3.0.
    (b) Examples of three conformations of $\LA$ (top) and $\LB$ (bottom)
}
\end{figure}
